### 2024-09-25 Notes/Notes.tex
Notes update

\begin{enumerate}
    \item Connectivity Indices: These indices quantify the degree of connectivity between atoms based on the topology of the molecule. Popular examples include the Randic index and the Balaban index.
    \item Information Indices: These are based on the concept of information theory, where the structure is interpreted as a distribution of information (or entropy). They measure molecular complexity and diversity.
    \item 2D-Matrix Based Descriptors: These descriptors use matrices (such as adjacency or distance matrices) derived from the 2D molecular graph. They help describe relationships between atoms in a molecule.
    \item 2D Autocorrelations: These descriptors calculate correlations between atomic properties at different distances in the molecular graph. They capture how molecular properties change across the structure.
    \item Burden Eigenvalues: These descriptors are derived from the eigenvalues of matrices related to the structure, such as the Burden matrix, which takes into account atomic properties like electronegativity and partial charges.
    \item P\_VSA-like Descriptors: P\_VSA stands for “Property-weighted Van der Waals Surface Area.” These descriptors quantify the surface area of a molecule associated with specific properties like polarizability or charge.
    \item ETA Indices (Extended Topochemical Atom): ETA indices capture aspects of molecular topology in conjunction with atomic properties. They are often used in the analysis of electronic properties or biological activities.
    \item Edge Adjacency Indices: These descriptors are derived from the adjacency of bonds (edges) in the molecular graph. They measure the proximity of bonds in the structure and can reflect molecular complexity.
    \item Fractional Group Counts: These descriptors count specific chemical groups or fragments within the molecule, providing information about the functional groups present.
    \item Atom-Centered Fragments: These descriptors focus on the environment of individual atoms within a molecule. They describe the types and arrangements of atoms surrounding each atom in the structure.
    \item Atom-Type E-State Indices: The E-State (Electrotopological State) descriptors combine information about the electronic environment and topology of atoms. They reflect the potential reactivity of atoms in the molecule.
    \item Pharmacophore Descriptors: These describe the spatial arrangement of features critical for molecular recognition by biological targets, such as hydrogen bond donors/acceptors, hydrophobic regions, or aromatic rings.
    \item 2D Atom Pairs: These descriptors capture the relationships between pairs of atoms at a specific distance (in terms of bonds) from each other. They describe the distribution of atom pairs within the molecular structure.
    \item Charge Descriptors: These describe the charge distribution within the molecule, including total charge, partial atomic charges, and the dipole moment.
    \item Molecular Properties: These include physical and chemical properties of the molecule such as molecular weight, boiling point, or solubility.
    \item Drug-Like Indices: These descriptors quantify how closely the molecule follows the rules for drug-likeness, such as Lipinski’s Rule of Five, which includes factors like molecular weight, hydrophobicity, and hydrogen bonding.
    \item MDE Descriptors (Molecular Distance Edge descriptors): These describe the distances between atoms in a molecule based on the molecular graph. They are useful for capturing molecular shape and spatial relationships.
    \item Chirality Descriptors: These quantify the chirality (handedness) of molecules. They reflect the 3D arrangement of atoms around chiral centers, which can influence how molecules interact with biological systems.
\end{enumerate}

>>>>

\begin{definition}
Connectivity Indices: Connectivity Indices are a class of molecular descriptors that quantify the connectivity or bonding patterns between atoms in a molecule based on its topology (i.e., the molecular graph). These indices capture the degree to which atoms are connected, considering how atoms are bonded to each other rather than their physical 3D arrangement. They are typically derived from graph theory, where atoms are represented as vertices and bonds as edges.\cite{connectivityIndicesArticle}
\end{definition}

\begin{definition}
Randic Index: Specific connectivity index defined as the following,
\begin{align}
\sum_{\text{all bonds}}\frac{1}{\sqrt{d_id_j}}
\end{align}
where $d_i$ and $d_j$ denote the number of bonds of atoms $i$ and $j$ connected by a bond.\cite{RandicIndexArticle}
\end{definition}

\begin{definition}
Information Indices: Kind of descriptor based on the information theory, where the molecular structure is represented as a distribution of information (or entropy). They measure molecular complexity and diversity.
\end{definition}

\begin{definition}
2D-Matrix Based Descriptors: Kind of descriptor based in the matricidal representation of a molecule\cite{DescriptorsBookClassification}. 
\end{definition}

\begin{definition}
Adjacency Matrix: Matricidal representation of a molecule. If we have $\{x\}_{i=1}^n$ atoms that form our molecule, labeled from 1 to n, the adjacent matrix $A$ will contain as the element $a_{i,j}$ 1 if the atom $i$ and $j$ are connected and 0 otherwise. (We can also naturally add the possibilities of $a_{i,j}=2,3$ for double and triple bonds).\par
For instant in the Figure (\ref{figurenButaneIsobutaneGraph}) the adjacent matrix for the n-Butane is
\begin{align}
\text{n-Butane AM}=\begin{pmatrix}
0 & 1 & 0 & 0 \\
1 & 0 & 1 & 0 \\
0 & 1 & 0 & 1 \\
0 & 0 & 1 & 0 
\end{pmatrix}
\end{align}
Trivially we observe that the main diagonal will always be filled with 0s and the matrices will also be doubly symmetrical (respect both diagonals) due to the bounds transitivity and reflectivities properties.
\end{definition}

\begin{enumerate}
    \item 2D Autocorrelations: These descriptors calculate correlations between atomic properties at different distances in the molecular graph. They capture how molecular properties change across the structure.
    \item Burden Eigenvalues: These descriptors are derived from the eigenvalues of matrices related to the structure, such as the Burden matrix, which takes into account atomic properties like electronegativity and partial charges.
    \item P\_VSA-like Descriptors: P\_VSA stands for “Property-weighted Van der Waals Surface Area.” These descriptors quantify the surface area of a molecule associated with specific properties like polarizability or charge.
    \item ETA Indices (Extended Topochemical Atom): ETA indices capture aspects of molecular topology in conjunction with atomic properties. They are often used in the analysis of electronic properties or biological activities.
    \item Edge Adjacency Indices: These descriptors are derived from the adjacency of bonds (edges) in the molecular graph. They measure the proximity of bonds in the structure and can reflect molecular complexity.
    \item Fractional Group Counts: These descriptors count specific chemical groups or fragments within the molecule, providing information about the functional groups present.
    \item Atom-Centered Fragments: These descriptors focus on the environment of individual atoms within a molecule. They describe the types and arrangements of atoms surrounding each atom in the structure.
    \item Atom-Type E-State Indices: The E-State (Electrotopological State) descriptors combine information about the electronic environment and topology of atoms. They reflect the potential reactivity of atoms in the molecule.
    \item Pharmacophore Descriptors: These describe the spatial arrangement of features critical for molecular recognition by biological targets, such as hydrogen bond donors/acceptors, hydrophobic regions, or aromatic rings.
    \item 2D Atom Pairs: These descriptors capture the relationships between pairs of atoms at a specific distance (in terms of bonds) from each other. They describe the distribution of atom pairs within the molecular structure.
    \item Charge Descriptors: These describe the charge distribution within the molecule, including total charge, partial atomic charges, and the dipole moment.
    \item Molecular Properties: These include physical and chemical properties of the molecule such as molecular weight, boiling point, or solubility.
    \item Drug-Like Indices: These descriptors quantify how closely the molecule follows the rules for drug-likeness, such as Lipinski’s Rule of Five, which includes factors like molecular weight, hydrophobicity, and hydrogen bonding.
    \item MDE Descriptors (Molecular Distance Edge descriptors): These describe the distances between atoms in a molecule based on the molecular graph. They are useful for capturing molecular shape and spatial relationships.
    \item Chirality Descriptors: These quantify the chirality (handedness) of molecules. They reflect the 3D arrangement of atoms around chiral centers, which can influence how molecules interact with biological systems.
\end{enumerate}
